l

### 2020-01-19 random/career_preparation/resume/resume.tex
gan going thru training but not really any results

%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------
\section{EXPERIENCE}
\textbf{Fermilab - LSST Machine Learning Intern\hfill Jun - Aug 2019}\\
\textbullet{Researched the applications of neural differential equations in astronomy for the Large Synoptic Survey Telescope (LSST)\\}
\textbullet{Used the PLAsTiCC Astronomical Kaggle dataset to train a neural network to approximate the differential equation of different astronomical objects' light curves (brightness over time)}\\
\textbullet{Presented poster of my work on Neural-ODEs at 2019 LSST Conference in Arizona}\\
\textbullet{Worked with peers and mentors to create a high level API for fast prototyping and ensemble training of neural networks for astronomy datasets, primarily in PyTorch}
\begin{itemize}
    \item \textbf{Tools:} TorchDiffEq, DifferentialEquations.jl, PyTorch, TensorFlow, Matplotlib, Astropy, Python, Julia
\end{itemize}
\section{PROJECTS}
\textbf{Sips: Sports Data Tool on Google Cloud\hfill Oct 2018 - Now}\\
\textbullet{Created Python package to track odds and statistics for a variety of sports\\}
\textbullet{Have collected over 1 GBs of data using Linux virtual machines on Google Cloud }\\
\textbullet{Trained TensorFlow win/loss classification and LSTM time-series prediction neural network models on Sips data}\\
\textbullet{Wrote Flask app to visualize odds using Matplotlib}
\begin{itemize}
\item \textbf{Tools:} Python, Requests, Beautiful Soup, TensorFlow, Flask, Matplotlib
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/sips
\end{itemize}
\textbf{Gym-Sips: Reinforcement Learning Environment\hfill Feb 2019 - Now}\\
\textbullet{Custom reinforcement learning environments using the OpenAI Gym package for the output data of sips}\\
\textbullet{Agent takes actions to buy the home team or the away team moneyline, and receives reward at the end of the game}\\
\textbullet{Agent learns risk mitigating hedging strategies}

>>>>

%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------
\section{EXPERIENCE}
\textbf{Fermilab - LSST Machine Learning Intern\hfill Jun - Aug 2019}\\
\textbullet{Researched the applications of neural differential equations in astronomy for the Large Synoptic Survey Telescope (LSST)\\}
\textbullet{Used the PLAsTiCC Astronomical Kaggle dataset to train a neural network to approximate the differential equation of different astronomical objects' light curves (brightness over time)}\\
\textbullet{Presented poster of my work on Neural-ODEs at 2019 LSST Conference in Arizona}\\
\textbullet{Worked with peers and mentors to create a high level API for fast prototyping and ensemble training of neural networks for astronomy datasets, primarily in PyTorch}
\begin{itemize}
    \item \textbf{Tools:} TorchDiffEq, DifferentialEquations.jl, PyTorch, TensorFlow, Matplotlib, Astropy, Python, Julia
\end{itemize}
\section{PROJECTS}
\textbf{Sips: Sports Data Tool on Google Cloud\hfill Oct 2018 - Now}\\
\textbullet{Attempting to deploy data scrapers that gather information about sports and the odds market, feed this data into different neural network architectures and evaluate model performance.\\}
\textbullet{Using Linux VMs on Google Cloud, I run Python scripts to track REST APIs for odds and sports statistics websites with BeautifulSoup}\\
\textbullet{Trained TensorFlow win/loss classification and LSTM time-series prediction neural network models on Sips data}\\
\textbullet{Wrote Flask app to visualize odds using Matplotlib}
\begin{itemize}
\item \textbf{Tools:} Python, Requests, Beautiful Soup, TensorFlow, Flask, Matplotlib
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/sips
\end{itemize}
\textbf{Gym-Sips: Reinforcement Learning Environment\hfill Feb 2019 - Now}\\
\textbullet{Custom reinforcement learning environments using the OpenAI Gym package for the output data of sips}\\
\textbullet{Agent takes actions to buy the home team or the away team moneyline, and receives reward at the end of the game}\\
\textbullet{Agent learns risk mitigating hedging strategies}
